Shape Inflation With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes

### 2013-04-26 documents/thesis/SIBGRAPI2013/TQLBO.tex

%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,review]{acmsiggraph}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amssymb}
\usepackage{graphicx}

\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
% for the following cases use the listed document class option:
% [annual] - Technical paper accepted for presentation at the ACM SIGGRAPH 
%   or SIGGRAPH Asia annual conference.
% [sponsored] - Short or full-length technical paper accepted for 
%   presentation at an event sponsored by ACM SIGGRAPH
%   (but not the annual conference Technical Papers program).
% [abstract] - A one-page abstract of your accepted content
%   (Technical Sketches, Posters, Emerging Technologies, etc.). 
%   Content greater than one page in length should use the "[sponsored]"
%   parameter.
% [preprint] - A preprint version of your final content.
% [review] - A technical paper submitted for review. Includes line
%   numbers and anonymization of author and affiliation information.

% When you submit your paper for review, please use the \TOGonlineID''
% command to include the online ID value assigned to your paper by the
% submission management system. Replace '45678' with the value you were
% assigned.
\TOGonlineid{XXXXX}

% If you are preparing a preprint of your accepted paper, and your paper
% will be published in an issue of the ACM "Transactions on Graphics''
% journal, replace the "0'' values in the commands below with the correct
% volume and number values for that issue - you'll get them before your
% final paper is due.
\TOGvolume{0}
\TOGnumber{0}

% The TOGarticleDOI' command accepts the DOI information provided to you
% during production, and which makes up the URLs which identifies the ACM
% article page and direct PDF link in the ACM Digital Library.
% Replace "1111111.2222222'' with the values you are given.
\TOGarticleDOI{1111111.2222222}

% If you would like to include links to personal repositories for auxiliary
% material related your research contribution, you may use one or more of
% these commands to define an appropriate URL. The "\TOGlinkslist'' command
% found just before the first section of your document will add hyperlinked
% icons to your document, in addition to hyperlinked icons which point to
% the ACM Digital Library article page and the ACM Digital Library-held PDF.
\TOGprojectURL{}
\TOGvideoURL{}
\TOGdataURL{}
\TOGcodeURL{}

% Paper title.
\title{Shape Enhanced With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}

% Author and Affiliation (single author).
%\author{Name \thanks{e-mail: name@unknown.uu}\\ Research Institute}

% Author and Affiliation (multiple authors).
\author{Alexander Pinzon\thanks{e-mail: apinzonf@gmail.com}
\qquad  Eduardo Romero\thanks{e-mail:edromero@unal.edu.co}
 \\Cimalab Research Group\\National University of Colombia}
%\and Ton Roosendaal\thanks{e-mail:ton@blender.org}\\ Blender CEO}

% The ``pdfauthor'' command accepts the authors of the work,
% comma-delimited, and adds this information to the PDF metadata.
%\pdfauthor{Alexander Pinzon, Eduardo Romero, Ton Roosendaal}
\pdfauthor{Anonymous}

% Keywords that describe your work.
\keywords{laplacian smooth, curvature, sculpting, subdivision surface}

\makeatother

\usepackage{babel}
\begin{document}

\teaser{\includegraphics[width=1\textwidth]{images/spectrum} \caption{\label{fig:Spectrum}A set of 48 successive shapes enhanced, from
$\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps of
$-5.0$.}
}

\maketitle
\maketitle 
\begin{abstract}
This paper proposes a novel modeling method for a hybrid quad/triangle
mesh that allows to set a family of possible shapes by controlling
a single parameter, the global curvature. The method uses an original
extension of the Laplace Beltrami operator that efficiently estimates
a curvature parameter which is used to define an enhanced shape after
a particular operation performed in certain mesh points. Along with
the method, this work presents new applications in sculpting and modeling,
with subdivision of surfaces and weight vertex groups. A series of
graphics examples demonstrates the quality, predictability and flexibility
of the method in a real production environment with software Blender.
\end{abstract}

\begin{CRcatlist}
\CRcat{I.3.5}{Computer Graphics}{Computational Geometry and Object Modeling
}{Modeling packages}
\end{CRcatlist}
\keywordlist

\TOGlinkslist

%\copyrightspace

\section{Introduction}

Over the last years several, modeling techniques able to generate
a variety of realistic shapes, have been developed \cite{Botsch2006}.
Editing techniques have evolved from affine transformations to advanced
tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
editing, creation from sketches \cite{Igarashi1999,Gonen2012}, and
complex interpolation techniques \cite{Sorkine2004,Zhou2005}. Catmull-Clark
based methods however require to interact with a minimun number of
control points for any operation to be efficient, or in other words,
a unicity condition is introduced by demanding a smooth surface after
any of these shape operations. Hence, traditional modeling methods
for subdividing surfaces from coarse geometry have become widely popular
\cite{Catmull1978,Stam1998}. These works have generalized a uniform
B-cubic spline knot insertion to meshes, some of them adding some
type of control, for instance with the use of creases to produce sharp
edges \cite{DeRose1998}, or the modification of some vertex weights
to locally control the zone of influence \cite{Biermann2000}. Neverteless
these methods are difficult to deal with since they require a large
number of parameters and a very tedious customization. Instead, the
presented method requires a single parameter that controls the global
curvature, which is used to maintain realistic shapes, creating a
family of different versions of the same object and therefore preserving
the detail of the original model and a realistic appearance.

@@

\textbf{Contributions} This work presents an extension of the Laplace
Beltrami operator for hybrid quad/triangle meshes, representing a
larger mesh spectrum from what has been presented so far. The method
eliminates the need of preprocessing and allows preservation of the
original topology. Likewise, along with this operator, it is proposed
a method to generate a family of parameterized shapes, in a robust
and predictable way. This method enables customization of the smoothness
and curvature, obtained during the subdivision surfaces process. Finally,
it is proposed a new brush for enhancing the silhouette mesh features
in modeling and sculpting.

@@

\section{Related work\label{sub:1.1-Related-work}}

Many tools have been developed for modeling, based on the Laplacian
mesh processing. Thanks to the advantages of the Laplacian operator,
these different tools preserve the surface geometric details when
using them for different processes such as free-form deformation,
fusion, morphing and other applications \cite{Sorkine2004}.

@@

\section{Laplacian Smooth\label{sec:Laplacian-Smooth}}

\begin{figure*}[t]
\includegraphics[width=1\textwidth]{images/beltrami}

@@

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{images/voronoi_region}

@@

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{images/quad_xiong}

@@

\begin{figure*}[t]
\includegraphics[width=1\textwidth]{images/teaser_cup}

@@

\begin{figure*}[t]
\includegraphics[width=1\textwidth]{images/cruz_lambda4}

@@

\begin{figure}
\includegraphics[width=1\columnwidth]{images/test_triangles_quads}

@@

\begin{figure}
\includegraphics[width=1\columnwidth]{images/camello_enhanced2}

@@

\begin{figure}
\includegraphics[width=1\columnwidth]{images/sculpt_brush}

@@

\begin{figure}
\includegraphics[width=1\columnwidth]{images/verts_per_second_sculpt}

@@

\begin{figure}
\includegraphics[width=1\columnwidth]{images/monkey}

@@

\begin{figure*}[t]
\includegraphics[width=1\textwidth]{images/camello_walk2}

@@

\section*{Acknowledgments}

We wold like to thank  anonymous friends for their support of our
research.

@@

Livingstone elephant model is provided courtesy of INRIA and ISTI
by the AIM@SHAPE Shape Repository. Hand model is courtesy of the FarField
Technology Ltd. Camel model by Valera Ivanov is licensed under a Creative
Commons Attribution 3.0 Unported License. Dinosaur and Monkey models
are under public domain, courtesy of Blender Foundation.

\bibliographystyle{acmsiggraph/acmsiggraph}
\bibliography{template}

@@

>>>>

\documentclass[10pt, conference]{IEEEtran}
\usepackage{subimages}
\setfigdir{figs}
\usepackage[cmex10]{amsmath}
\interdisplaylinepenalty=2500
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{graphicx}
\newtheorem{definition}{Definition}
%\usepackage{hyperref}

\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
\title{Shape Inflation With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}

%------------------------------------------------------------------------- 
% change the % on next lines to produce the final camera-ready version 
\newif\iffinal
%\finalfalse
\finaltrue
\newcommand{\jemsid}{99999}
%-------------------------------------------------------------------------

\iffinal
  \author{%
    \IEEEauthorblockN{Alexander Pinzon, Eduardo Romero}
    \IEEEauthorblockA{%
      Cimalab Research Group\\
      Universidad Nacional de Colombia\\
      Bogota-Colombia\\
      %Email: \href{mailto:apinzonf@unal.edu.co}{apinzonf@unal.edu.co}, \href{mailto:edromero@unal.edu.co}{edromero@unal.edu.co}
      Email: apinzonf@unal.edu.co, edromero@unal.edu.co }
  }
\else
  \author{Sibgrapi paper ID: \jemsid \\ }
\fi

\teaser{%
  \oneimage{\label{fig:Spectrum} A set of 48 successive shapes enhanced, from
$\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps of
$-5.0$.}{.99}{spectrum}
}

\maketitle

\begin{abstract}
This paper proposes a novel modeling method for a hybrid quad/triangle
mesh that allows to set a family of possible shapes by controlling
a single parameter, the global curvature. The method uses an original
extension of the Laplace Beltrami operator that efficiently estimates
a curvature parameter which is used to define an inflated shape after
a particular operation performed in certain mesh points. Along with
the method, this work presents new applications in sculpting and modeling,
with subdivision of surfaces and weight vertex groups. A series of
graphics examples demonstrates the quality, predictability and flexibility
of the method in a real production environment with software Blender.

\end{abstract}

\begin{IEEEkeywords}
laplacian smooth; curvature; sculpting; subdivision surface

\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\section{Introduction}
%
Over the last years several, modeling techniques able to generate
a variety of realistic shapes, have been developed \cite{Botsch2006}.
Editing techniques have evolved from affine transformations to advanced
tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
editing, creation from sketches \cite{Igarashi1999,Gonen2012}, and
complex interpolation techniques \cite{Sorkine2004,Zhou2005}. Catmull-Clark
based methods however require to interact with a minimun number of
control points for any operation to be efficient, or in other words,
a unicity condition is introduced by demanding a smooth surface after
any of these shape operations. Hence, traditional modeling methods
for subdividing surfaces from coarse geometry have become widely popular
\cite{Catmull1978,Stam1998}. These works have generalized a uniform
B-cubic spline knot insertion to meshes, some of them adding some
type of control, for instance with the use of creases to produce sharp
edges \cite{DeRose1998}, or the modification of some vertex weights
to locally control the zone of influence \cite{Biermann2000}. Neverteless
these methods are difficult to deal with since they require a large
number of parameters and a very tedious customization. Instead, the
presented method requires a single parameter that controls the global
curvature, which is used to maintain realistic shapes, creating a
family of different versions of the same object and therefore preserving
the detail of the original model and a realistic appearance.

@@

%------------------------------------------------------------------------- 
\paragraph*{Contributions}
%
This work presents an extension of the Laplace
Beltrami operator for hybrid quad/triangle meshes, representing a
larger mesh spectrum from what has been presented so far. The method
eliminates the need of preprocessing and allows preservation of the
original topology. Likewise, along with this operator, it is proposed
a method to generate a family of parameterized shapes, in a robust
and predictable way. This method enables customization of the smoothness
and curvature, obtained during the subdivision surfaces process. Finally,
it is proposed a new brush for enhancing the silhouette mesh features
in modeling and sculpting.

@@

%------------------------------------------------------------------------- 
\subsection{Related work\label{sub:1.1-Related-work}}
%
Many tools have been developed for modeling, based on the Laplacian
mesh processing. Thanks to the advantages of the Laplacian operator,
these different tools preserve the surface geometric details when
using them for different processes such as free-form deformation,
fusion, morphing and other applications \cite{Sorkine2004}.

@@

%==========================================
\section{Laplacian Smooth\label{sec:Laplacian-Smooth}}
%
\begin{figure*}[t]
\includegraphics[width=1\textwidth]{figs/beltrami}

@@

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{figs/voronoi_region}

@@

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{figs/quad_xiong}

@@

\begin{figure*}[t]
\includegraphics[width=1\textwidth]{figs/teaser_cup}

@@

\begin{figure*}[t]
\includegraphics[width=1\textwidth]{figs/cruz_lambda4}

@@

\begin{figure}
\includegraphics[width=1\columnwidth]{figs/test_triangles_quads}

@@

\begin{figure}
\includegraphics[width=1\columnwidth]{figs/camello_enhanced2}

@@

\begin{figure}
\includegraphics[width=1\columnwidth]{figs/sculpt_brush}

@@

\begin{figure}
\includegraphics[width=1\columnwidth]{figs/verts_per_second_sculpt}

@@

\begin{figure}
\includegraphics[width=1\columnwidth]{figs/monkey}

@@

\begin{figure*}[t]
\includegraphics[width=1\textwidth]{figs/camello_walk2}

@@

%==========================================
\iffinal
% use section* for acknowledgement
\section*{Acknowledgment}
%
We wold like to thank  anonymous friends for their support of our
research.

@@

Livingstone elephant model is provided courtesy of INRIA and ISTI
by the AIM@SHAPE Shape Repository. Hand model is courtesy of the FarField
Technology Ltd. Camel model by Valera Ivanov is licensed under a Creative
Commons Attribution 3.0 Unported License. Dinosaur and Monkey models
are under public domain, courtesy of Blender Foundation.
\fi

%==========================================

\bibliographystyle{IEEEtran}
\bibliography{template}

@@

%==========================================
